Dutch, PPs, ʀ-pronouns

### 2019-12-20 paper.tex
after 20.12
not much more
but convinced pavel of complementary distribution
look for a place for sigma

@@

This paper: \tit{waarmee} is the default realization of an instrumental when all features form a constituent. If not, then \tit{met wat}. The \tit{r} in ʀ-pronouns does not necessarily express \tsc{locative}, in \tit{waarmee} is only expresses \tsc{thing}. The change of \tit{met} into \tit{mee} is a reflex of stranded features/a different spellout of features.

@@

\section{Conditions for \tit{waarmee} and \tit{met wat} to appear}

@@

 \tit{Waarmee} is ʀ-pronoun, a term introduced by \cite{riemsdijk1978}. ʀ-pronouns are not specific to the inanimate relative pronouns. No inanimate pronominal elements in Dutch is able to act as the object of a preposition. They are all replaced by an ʀ-pronoun. As suggested by the name, ʀ-pronouns always contain the morpheme \tit{r}.

@@

What this shows is that in principle \tit{waarmee} is used, it is the default. There is something special about the examples in which \tit{met wat} is used.

@@

\ex.
\ag. Ik heb gekocht [waar jij mee schildert].\\
 I have bought where you with paint\\
 `I bought what you are painting with.'
\bg. *Ik heb gekocht [met wat jij schildert].\\
 I have bought with what you paint\\
 `I bought what you are painting with.'

@@

@@

\ex. \begin{forest} boom
[
    [waarmee]
    [schildert]
]
\end{forest}

\ex. \begin{forest} boom
[
    [jij]
    [
        [waarmee]
        [schildert]
    ]
]
\end{forest}

\ex. \begin{forest} boom
[
    [jij]
    [
        [
            [waar]
            [mee]
        ]
        [schildert]
    ]
]
\end{forest}

now move \tit{waar}

\ex. \begin{forest} boom
[
    [waar]
    [
        [jij]
        [
            [
                [mee]
            ]
            [schildert]
        ]
    ]
]
\end{forest}

or \tit{waarmee}

\ex. \begin{forest} boom
[
    [
        [waar]
        [mee]
    ]
    [
        [jij]
        [
            [schildert]
        ]
    ]
]
\end{forest}

@@

Now I repeat the \tit{met wat} example.

\ex.
\ag. *Ik schilder [waar]mee [jij hebt gekocht].\\
 I paint {where with} you have bought\\
 `I paint with what you bought.'
\bg. Ik schilder met [wat jij hebt gekocht].\\
 I paint with what you have bought\\
 `I paint with what you bought.'

@@

How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spellout. Something interevened. More examples of that.

@@

>>>>

Mismatching free relatives give a unique insight into the internal structure of r-pronouns.

@@

This paper: \tit{waarmee} is the default realization of an instrumental when all features form a constituent. If not, then \tit{met wat}. The \tit{r} in ʀ-pronouns does not necessarily express \tsc{location}, in \tit{waarmee} is only expresses \tsc{thing}. The change of \tit{met} into \tit{mee} is a reflex of stranded features/a different spellout of features.

@@

\section{\tit{\tsc{r}}-pronouns as default \\
Distribution between \tit{waarmee} and \tit{met wat}}

@@

 \tit{Waarmee} is an ʀ-pronoun, a term introduced by \cite{riemsdijk1978}. ʀ-pronouns are not specific to the inanimate relative pronouns. No inanimate pronominal elements in Dutch is able to act as the object of a preposition. They are all replaced by an ʀ-pronoun. As suggested by the name, ʀ-pronouns always contain the morpheme \tit{r}.

@@

What this shows is that ʀ-pronouns are not exceptions, but they are the default. There is something special about the examples in which \tit{met wat} is used. I suggest that the crucial difference lies in constituency. \tit{Waarmee} can only be used if the instrumental PP forms a proper constituent, i.e. a constituent to the exclusion of any other elements. In the examples from xx to xx above this is the case.

Let me now show how this applies to the examples with the mismatching relatives.

@@

@@

\ex. \begin{forest} boom
[
    [
        [gekocht, roof]
    ]
    [
        [waar jij mee schildert, roof]
    ]
]
\end{forest}

@@

\ex. \begin{forest} boom
[
    [
        [met, roof]
    ]
    [
        [wat jij hebt gekocht, roof]
    ]
]
\end{forest}

@@

@@

How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spell out.

@@

Van Riemsdijk said that R-pronouns are pronouns and they orginate in the complement of P. Due to \tsc{r}-movement they move to the spec of PP, and due to suppletion they change form, coincidentally to something identical to the locative. Full DPs cannot move to the spec of PP because they do not have access to that spec.

I claim that this movement is not a special r-movement, but a movement driven by spellout. The suppletion also follows from the regular spellout algorithm, and it is the locative that is inserted.

Koopman's account differ from Van Riemsdijk's in that she assumes \tsc{r}-pronouns obligatorily move to specPlace. The fact that locatives and \tsc{r}-pronouns are syncretic is not a surprise. They occur in the same structural configuration.

Place does not make a lot of sense in \tit{waarmee}, because we do not have a place here.

Abels says that this movement from the complement to the spec is not allowed. He argues that, instead, that R-words are base generated as the specifiers of distinguished class of zero-place prepositions. \tsc{r} is the complement of P and is subextracted from the complement of P (which is allowed, because it is subextraction and not extraction of it as a whole.)

I agree with Abels in that \tit{r} is substracted from the complement of the preposition. However, I say that \tit{r} is actually the pronoun. What he refers to as an \tsc{r}-word is in Dutch \tit{w-aa-}, which I also assume is merged later.

I do not care whether \tit{w-} and \tit{-a-} are merged before or after.

WHY DOES MEE MOVE? I DO NOT KNOW.
BUT IT DOES.
AND SO DOES WAAR.
waar maybe because it is remnant movement?
